\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
notation changed

\begin{abstract}
Understanding how the brain works is a key
to treat brain disorders such as Parkinson's disease,
epilepsy. Retrieving connectomes, the neurons wiring map, will shed a new
light on the anatomical and functional connectivity of the brain. In the
context of the Connectomics challenge, we propose a simple algorithm made of
four stages, using preprocessing and partial correlation to achieve a network
inference of high quality. An optimized variation of this simple algorithm
is the winning method of the Connectomics Challenge.

We put in perspective our method
with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
(\cite{huynhthu2010inferring}).

@@

\textcolor{red}{As it can be seen on \textit{fig 1}, the raw signal is very noisy and
a low-pass filter is therefore applied to get a cleaner version of the signal where only
true variations are kept, i.e. without noise variations. However, the choice of a low-pass
filter is not unique. In the rest of the paper, we will focus on two types, the
symmetrical median filter, i.e., $X_t^i \leftarrow X_{t-1}^i + X_{t}^i + X_{t+1}^i$,
and an asymmetrical weighted median filter, i.e.,
$X_t^i \leftarrow 0.4 X_{t-3}^i + 0.6 X_{t-2}^i + 0.8 X_{t-1}^i + X_{t}^i$.}\\

\textcolor{red}{Considering the short delay for a communication between
neurons, slow events can be neglected to retrieve direct relationships.
Indeed, for a direct relationship, i.e. a neuron firing directly implying another
neuron to fire, the average time is about $1ms$ or $2ms$ while the
fluorescent signal time resolution is $20ms$. In order to find out which neurons
are directly related, it is only necessary to look after the burst signal, or
in other words, whether the signal varies. In our approach, we choose to apply
an asymmetrical discrete derivative : $X_{t,d}^{i} \leftarrow X_{t}^i - X_{t-1}^i$.}\\

\textcolor{red}{By nature, the firing event is really fast and in order to
retrieve the connectivity from them, it is necessary to link a burst to a
couple of timesteps (ideally one). The small decay for the fluorescent calcium
indicator implies a signal variation during a long interval and therefore, in
order to only keep rising and strong transitions, we apply a hard-tresholing filter:
$X_{t,d}^i = X_{t,d}^i \mathbb{1}(X_{t,d}^i \geq \tau)$ where $\tau$ is a given threshold.
As a result, we get a binary-like signal with the true activity when a burst
happens and with a true zero when the neuron is inactive.}

>>>>

\begin{abstract}
Understanding how the brain works is a key
to treat brain disorders such as Parkinson's disease,
epilepsy. Retrieving connectomes, the neurons wiring map, will shed a new
light on the anatomical and functional connectivity of the brain. In the
context of the Connectomics challenge, we propose a simple algorithm made of
four stages, using preprocessing and partial correlation to achieve a network
inference of high quality. An optimized variation of this simple algorithm
is the winning method of the Connectomics Challenge.
We put in perspective our method
with other inference methods such as GTE (\cite{stetter2012model}) and Genie3
(\cite{huynhthu2010inferring}).

@@

\textcolor{red}{As it can be seen on \textit{fig 1}, the raw signal is very noisy and
a low-pass filter is therefore applied to get a cleaner version of the signal where only
true variations are kept, i.e. without noise variations. However, the choice of a low-pass
filter is not unique. In the rest of the paper, we will focus on two types, the
symmetrical median filter, i.e., $x^t_i \leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i$,
and an asymmetrical weighted median filter, i.e.,
$x^t_i \leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + X^{t}_i$.}\\

\textcolor{red}{Considering the short delay for a communication between
neurons, slow events can be neglected to retrieve direct relationships.
Indeed, for a direct relationship, i.e. a neuron firing directly implying another
neuron to fire, the average time is about $1ms$ or $2ms$ while the
fluorescent signal time resolution is $20ms$. In order to find out which neurons
are directly related, it is only necessary to look after the burst signal, or
in other words, whether the signal varies. In our approach, we choose to apply
an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - X^{t-1}_i$.}\\

\textcolor{red}{By nature, the firing event is really fast and in order to
retrieve the connectivity from them, it is necessary to link a burst to a
couple of timesteps (ideally one).

The small decay for the fluorescent calcium
indicator implies a signal variation during a long interval and therefore, in
order to only keep rising and strong transitions, we apply a hard-tresholing filter:
$x^{t,d}_i = X^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where $\tau$ is a given threshold 
As a result, we get a binary-like signal with the true activity when a burst
happens and with a true zero when the neuron is inactive.}
